Corotating Dust Clumps Around Adolescent M-Dwarfs: Four Years of TESS

### 2023-06-25 paper/ms.tex
update ms

%%%%%%%%%
% STARS %
%%%%%%%%%
\newcommand{\nstarssearched}{{XXYYY}}

@@

For the SED fitting, we use \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}, tuned to use only the BT-Settl stellar
atmosphere models \citep{Allard2012} based on the
\citet{2009ARA&A..47..481A} solar abundances.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, $riz$ from
Pan-STARRS1, SDSS $riz$, and the WISE 1-2 passbands.  We specifically
omitted UV flux measurements to avoid biasing our fit with any
possible chromospheric UV excess.
\texttt{astroARIADNE} compares the measured broadband flux measurements
against pre-computed model grids, and by default fits for six
parameters:
$\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm Fe/H}], d \}$.
The distance  prior is drawn from \citet{2021AJ....161..147B}.
The surface gravity and metallicity are generally unconstrained.
And finally, given our particular use-case, 
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.0), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.
Using \texttt{Dynesty} \citep{2020MNRAS.493.3132S},
we statically sampled the posterior probability assuming the default
Gaussian likelihood, and set a stopping threshold of ${\rm d}\log
\mathcal{Z} < 0.01$, for $\mathcal{Z}$ the evidence.

@@

>>>>

%%%%%%%%%
% STARS %
%%%%%%%%%
\input{vals_searched_stars}

@@

For the SED fitting, we use \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}, tuned to use only the BT-Settl stellar
atmosphere models \citep{Allard2012} based on the
\citet{2009ARA&A..47..481A} solar abundances.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, $riz$ from
Pan-STARRS1, SDSS $riz$, and the WISE 1-2 passbands.  We specifically
omitted UV flux measurements to avoid biasing our fit with any
possible chromospheric UV excess.
\texttt{astroARIADNE} compares the measured broadband flux measurements
against pre-computed model grids, and by default fits for six
parameters:
$\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm Fe/H}], d \}$.
The distance  prior is drawn from \citet{2021AJ....161..147B}.
The surface gravity and metallicity are generally unconstrained.
And finally, given our particular use-case, 
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / {\rm R}_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.
Using \texttt{Dynesty} \citep{2020MNRAS.493.3132S},
we statically sampled the posterior probability assuming the default
Gaussian likelihood, and set a stopping threshold of ${\rm d}\log
\mathcal{Z} < 0.01$, for $\mathcal{Z}$ the evidence.

@@

\paragraph{Interpretation of the $T\lesssim 15$ dropoff}
Our search sample included 35472 unique stars with $12<T<14$, versus
2045 unique stars with $15<T<16$.  This helps clarify why our detected
CPVs become less common toward fainter TESS magnitudes, despite the
relative ease of their detectability, even at $15<T<16$.  It is
because the TESS 2-minute data are very incomplete at the faint end.
